Elaboration with First-Class Implicit Function Types

### 2020-02-17 paper.tex
pruning

Metacontexts are used to record metavariables which are created during
elaboration. In our case, metacontexts are simply a context prefix, and we have
variables pointing into it, but we do not support any contextual modality
e.g.\ as in \cite{nanevski2008contextual}. The non-meta typing context
additionally supports \emph{defined variables}, which is used in the typing rule
for \emph{let-definitions}, and we have that any defined variable is equal to
its definition. We mainly support this as a convenience feature in the
implementation of our elaborator.

>>>>

Metacontexts are used to record metavariables which are created during
elaboration. In our case, metacontexts are simply a context prefix, and we have
variables pointing into it. This corresponds to a particularly simple variant of
\emph{crisp type theory} \cite{licata2018internal}, where we do not have modal
type operators or functions with crisp (``meta'') domain. The non-meta typing context
additionally supports \emph{defined variables}, which is used in the typing rule
for \emph{let-definitions}, and we have that any defined variable is equal to
its definition. We mainly support this as a convenience feature in the
implementation of our elaborator.
